Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-27 doc/JFLA2022/paper.tex
less verbose paragraph on Gaia Bridge

\section{Main features}

\subsection{The Coq-Community ecosystem}
\begin{todo}
Small presentation.
\end{todo}

@@

\section{Conclusion and perspectives}

@@

The Gaia project~\cite{Gaia}, also maintained on \textit{Coq-Community} contains a development by José Grimm~\cite{grimm:hal-00911710}. This library -- dedicated  to the implementation in \textit{Coq (SSreflect)} of books from  Bourbaki's Elements of Mathematics --- contains a generalization of two types of ordinals (\texttt{T1} for the ordinal $\epsilon_0$ and
\texttt{T2} for $\Gamma_0$) to a larger ordinal defined by Ackermann, and relates these data structures with Bourbaki's set theory.
It is interesting to note that both libraries \textit{Gaia} and \textit{hydra-battles} contain their own (isomorphic but not identical) definitions of types \texttt{T1} and \texttt{T2}, both originated in~\cite{CantorContrib}.
Our plan is to build a  bridge between  the combinatorial results of \textit{hydra-battles} and the set-theoretic content of \textit{Gaia}, and make possible the transfer of theorems from one of the two libraries to the other one.

Another direction would be to write in \textit{Coq} a formal proof of the original statement of Theorem~\ref{kp:thm2}. For this purpose, we plan to import  the formalization of Peano Arithmetic by O'Connor~\cite{Goedel}.

>>>>

\section{Integration within Coq-Community}

\subsection{Presentation}

\subsection{Interactions with other Coq-Community projects}

@@

\subsection{Continuous integration and deployment, opam packaging, etc.}
\section{Conclusion and perspectives}

\TODO{General Conclusion}

@@

\subsection{Further extensions}

We plan to extend our libraies in two main directions.
The Gaia project~\cite{Gaia}, also maintained on \textit{Coq-Community} contains a development by José Grimm~\cite{grimm:hal-00911710}. This library is dedicated  to the implementation in \textit{Coq (SSreflect)} of books from  Bourbaki's Elements of Mathematics. It contains data structures which are compatible with our ordinal notations. 
Our plan is to build a  bridge between  the combinatorial results of \textit{hydra-battles} and the set-theoretic content of \textit{Gaia}, and make possible the transfer of theorems between both libraries.
Another direction would be to write in \textit{Coq} a formal proof of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.
